Development and Implementation of an ANN Based Flow Law for Numerical Simulations of Thermo-Mechanical Processes at High Temperatures in FEM Software

### 2023-01-13 Article.tex
Corrected proofs

%=================================================================
\documentclass[algorithms,article,submit,pdftex,moreauthors]{Definitions/mdpi}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{}
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{}
\datepublished{}
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

\usepackage{gensymb}
%\usepackage{amsmath}
\usepackage{accents}
%\usepackage{multirow}
\usepackage{xspace}
\usepackage{subcaption}
\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
\DeclareRobustCommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
\DeclareRobustCommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\DeclareRobustCommand{\Dev}{\mbox{\Large\ensuremath{\mathsf{s}}}}
\DeclareRobustCommand{\Sig}{\mbox{\Large\ensuremath{\sigma}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\MSE}{\text{E}_\text{MS}}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Development and Implementation of an ANN based flow law for Numerical Simulations of Thermo-mechanical Processes at High Temperatures in FEM Software}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Development and Implementation of an ANN based flow law for Numerical Simulations Thermo-mechanical Processes at High Temperatures in FEM Software}

@@

% Authors, for the paper (add full first names)
\Author{Olivier Pantalé \orcidA{}}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Olivier Pantalé}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Pantalé, O.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [XX] after \address if there is only one affiliation.)
\address[1]{Laboratoire Génie de Production, Institut National Polytechnique/Ecole Nationale d'Ingénieurs de Tarbes, Université de Toulouse, 47 Av d'Azereix, F-65016, Tarbes, France}

% Contact information of the corresponding author
\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Numerical methods based on Finite Element (FE) have proven their efficiency for many years in the thermomechanical simulation of forming processes.
Nevertheless, the application of these methods to new materials requires the identification and implementation of constitutive and flow laws within FE codes which sometimes pose problems, in particular because of the strongly non-linear character of the behavior of these materials.
Computational techniques based on Machine Learning and Artificial Neural Networks are becoming more and more important in the development of these models and help the FE codes to integrate more complex behavior.
In this paper, we present the development, implementation and use of an Artificial Neural Network (ANN) based flow law for a GrC15 alloy under high temperature thermomechanical solicitations.
The flow law modeling by ANN shows a significant superiority in terms of model prediction quality compared to classical approaches based on widely used Johnson-Cook or Arrhenius models.
Once the ANN parameters have been identified on the base of experiments, the implementation of this flow law in a Finite Element code shows promising results in terms of solution quality and respect of the material behavior.}

% Keywords
\keyword{ANN flow law; Constitutive behavior; Radial Return algorithm; Numerical implementation; VUHARD ; GrC15; Abaqus Explicit}

@@

Numerical methods for simulating the behavior of structures subjected to high thermomechanical loads, as in the case of high-temperature forming of metallic materials, are generally based on the use of commercial Finite Element (FE) codes such as Abaqus or laboratory codes such as DynELA \cite{Pantale-2004}.
These FE codes are based on two types of equations: conservation equations and constitutive equations.
If the first equations are well established on the basis of physics and mechanics, it is not the same for the second type of equations: the constitutive equations.
Thus, in a general way, the conservation equations concern the fundamental principles of physics such as the mass conservation law, the momentum law (fundamental equation) and the energy law (declined as the first and second principles of thermodynamics).
By themselves, these laws are not sufficient to describe the behavior of a material or a structure subjected to thermomechanical solicitations, because the nature of the material’s behavior translated through the behavior laws, is not included in the system previously proposed.
Therefore, for each type of material, it is necessary to define behavior laws whose formulation is based on observation, in order to describe the behavior of this material under external forces.
The quality and the accuracy of the results of any numerical simulation depend on the choice of these behavior laws and on the ability of the user to identify the coefficients of these behavior laws for a given material by performing experiments under conditions close to those encountered during the real stress of the structure in service that one wishes to design \cite{Dey-2007}.
Depending on the nature of the solicitations, these tests are based on quasi-static or dynamic tensile or compression tests, tests on thermomechanical simulators such as Gleeble \cite{Lin-2009} or impact tests using gas launchers or Hopkinson bars \cite{Kolsky-1949}.

In thermomechanical simulation of forming processes, these behavior laws define the dependence \cite{Lee-2006} of the flow stress of the material $\sigma^y$ as a function of the three input variables which are the plastic strain $\varepsilon^p$, the strain rate $\mdot\varepsilon$ and the temperature $T$ of the material, so that the general form of the flow law can be written with the following expression:
\begin{equation}
\sigma^y = f\left(\varepsilon^p,\mdot\varepsilon,T\right)\label{eq:GenFlow}
\end{equation}

These laws, due to the nature of materials and the phenomena involved \cite{Lennon-2004, Zhang-2012} (work hardening, movement of dislocations, structural hardening, phase transformations,...) are highly non-linear and their validity is restricted to a certain range of strains $\varepsilon$, strain rates $\mdot\varepsilon$ and temperatures $T$.
From the observations made, we can define two main classes of behavior laws: the flow laws based on physics and the empirical flow laws.
From the mechanics of continuous media and experimental tests and depending on the materials used, several flow models have been developed in the past, including: the Johnson-Cook flow law \cite{Johnson-1983, Johnson-1988}, the Zerilli Armstrong flow law \cite{Zerilli-1987} and their respective derived forms \cite{Lin-2011, Li-2013, Zhang-2015, Zhou-2020, Jia-2021, Rule-1998, Lin2010, Muralli-2017, Cheng-2021}, the Hansel-Spittle \cite{Hensel-1978, Chadha-2018} or the Arrhenius \cite{Jonas-1969, He-2013, Liang-2022} flow laws, to name only a few of the most widely used in the metal forming processes at high temperature.
As an example, and because it is widely used in numerical simulation of metal forming processes, the equation that describes the Johnson-Cook flow law \cite{Johnson-1983} is given as follows:
\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}.

Once the choice has been made concerning the type of flow law to be used for a material, it is then necessary, from a set of experimental tests carried out in the laboratory under conditions close to those of the structure in service, to identify the parameters of these flow laws by machine learning methods based on approaches of minimization of the calculated experiment.
Therefore, the use of the Johnson-Cook flow law defined by Equation (\ref{eq:Johnson-Cook}) require the identification of $5$ material parameters.

The main problem that the researchers are confronted with after the phase of realization of the experimental tests concerns the choice of the flow law to use according to the observations made on these test results.
This choice of flow law is also restricted by the FE code used and the availability of such flow laws.
Thus, a user of the Abaqus FE code, will turn more particularly to a Johnson-Cook \cite{Johnson-1983} flow law where it is natively implemented in this software.
The choice of another form of flow law, Zerilli-Armstrong, or Arrhenius for example, obliges the user to program himself the computation of the flow stress $\sigma^y$ of the material through a VUMAT subroutine in FORTRAN 77 as proposed by Gao \eal \cite{Gao-2007-FRT}, Ming \eal \cite{Ming-2018} for a Johnson-Cook flow law or Liang \eal \cite{Liang-2022} for an Arrhenius type flow law with the following expression:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{Z(\varepsilon)}{A(\varepsilon)}\right)^{1/n(\varepsilon)} + \sqrt{1 + \left(\frac{Z(\varepsilon)}{A(\varepsilon)}\right)^{2/n(\varepsilon)}}\right\}
\label{eq:ArDef}
\end{equation}
with:
\begin{equation}
Z(\varepsilon) = \mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}, \label{eq:ArZ}
\end{equation}
where $Z$ is the Zenner-Hollomon parameter \cite{Zener-1944}, $Q(\varepsilon)$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$).
$Q(\varepsilon)$, $A(\varepsilon)$, $\alpha(\varepsilon)$ and $n(\varepsilon)$ are expressed as a function of the strain $\varepsilon$ through polynomial functions of degree $m$ (varying from $1$ to $9$), which leads to the identification of up-to $36$ material parameters.

Implementing the flow law as a VUMAT FORTRAN subroutine requires the computation of the derivatives  $\partial\sigma^y/\partial\varepsilon^p$, $\partial\sigma^y/\partial\mdot\varepsilon$ and $\partial\sigma^y/\partial T$ of the flow stress $\sigma^y$ which can quickly become relatively complex as the complexity of the flow law increases, \ie the relative complexity of the Arrhenius flow law defined by Equations (\ref{eq:ArDef}) and (\ref{eq:ArZ}), regarding the relative simplicity of the Johnson-Cook defined by Equation (\ref{eq:Johnson-Cook}), one can refer to the work proposed by Liang \eal \cite{Liang-2022} for details concerning this implementation using the Safe version of the Newton-Raphson method proposed by Ming \eal \cite{Ming-2018}.
The choice of the flow law to use for a problem, is therefore doubly guided by the behavior of the material on the one hand, but a more important aspect is the list of flow laws implemented natively in the FE code we plan to use for the numerical simulation.
At this time, there is not yet a flow law generic enough to cover a wide range of material behavior that is simple to implement and use.

As we have seen in the previous paragraph, the choice of the flow law to use is guided mainly by the list of flow laws available in the Finite Element code used, and very often this choice is made at the expense of the quality of the model.
For example, Zhou \eal \cite{Zhou-2020}, proposed the identification of the flow law of a GCr15 alloy for a continuous casting bloom with heavy reduction application as introduced by Ji \eal \cite{Ji-2018} who have performed compression tests on this material.
In their study, Ji \eal \cite{Ji-2018} performed compression tests on GCr15 cylinders in a temperature range of $750~\celsius$ to $1300~\celsius$ in $50~\celsius$ steps, strain rates of $0.001~\ps$,  $0.01~\ps$ and $0.1~\ps$ and strains up-to $0.7$.
The results of these compression tests, plotted in Figure \ref{fig:Zhou-OriginalData}, show a decrease in flow stress $\sigma^y$ with respect to an increase of the temperature $T$ and a increase of $\sigma^y$ with respect to an increase of the strain rate $\mdot\varepsilon$, as in most metallic materials.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/Zhou-OriginalData}
\caption{Original data extracted from the publication of Ji \eal \cite{Ji-2018}.}
\label{fig:Zhou-OriginalData}
\end{figure}
The evolution of the flow stress as a function of the plastic deformation shows the presence of a dynamic recrystallization (DRX) phenomenon within the material.
This phenomenon is an additional non-linearity of this type of material compared to other materials, mainly because of high temperatures and low strain rates, which should be considered when describing the material behavior.
As stated in the publication of Zhou \eal \cite{Zhou-2020}, depending on the flow model used: Johnson-Cook, Modified Zerilli-Armstrong, Arrhenius or new Modified Johnson-Cook, the fidelity of considering the real behavior varies widely with the complexity of the flow model which includes between $5$ parameters for the Johnson-Cook model, and $16$ parameters for the Arrhenius model.
Thus, and for the input data provides by Ji \eal \cite{Ji-2018}, the two most common models: Johnson-Cook and Zerilli-Armstrong do not correctly describe the material behavior.
Only the modified Johnson-Cook and Arrhenius models can describe correctly the behavior of the material during the compression process.
Unfortunately, and this is not part of their study, if these last two models are satisfactory from a theoretical point of view, from a practical point of view for the user of a FE code such as Abaqus, it will be necessary to carry out a numerical implementation in a FORTRAN 77 VUMAT subroutine of the Modified Johnson-Cook flow law or the Arrhenius law as carried out by few authors \cite{Liang-2022, Gao-2007-FRT, Ming-2018} to use these laws for numerical simulation.
This requires a certain expertise in the development and implementation of flow laws, which is not available to all users of the Abaqus FE code.

From this observation, and from the necessity to select a flow law for a type of material, then to identify the parameters of this flow law according to experimental tests, and finally to implement this flow law as a user subroutine in FORTRAN in the Abaqus FE code, we have recently proposed in Pantalé \eal \cite{Pantale-2021} an alternative approach based on the ability of Artificial Neural Networks (ANNs) to behave as universal approximators as reported by Minsky \eal \cite{Minsky-1969} and Hornik \eal \cite{Hornik-1989}.
In fact, Artificial Neural Networks can solve problems that are difficult to conceptualize using traditional computational methods.
Unlike a classical approach based on a regression method, an ANN does not need to know the mathematical form of the model it seeks to reproduce, hence we do not need anymore to postulate the mathematical form of the constitutive equation to use it in a FE simulation using this kind of approach.
Using a Neural Network instead of an analytical constitutive law can lead to a bias related to the validity of the answers according to the domain of use and the learning domain.
Thus, if ANNs are efficient for the interpolation of results inside the learning domain, their behavior outside of it is not controlled.
Therefore, if the input values are far from those provided during the training, the outputs can be far from the physical reality of the process.
It is, of course, the same for analytical laws when modeling non-linear behavior, but if the choice of the model has been made properly, based on physical considerations, they will provide results closer to reality than the ANN model.
Therefore, care should be taken when using ANN-based flow laws and the validity of the model input data should always be verified.

>>>>

%=================================================================
\documentclass[algorithms,article,accept,pdftex,moreauthors]{Definitions/mdpi}
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{{ Xiang Zhang, Xiaoxiao Li } %MDPI: please add the academic editors.
}
\datereceived{16 December 2022}
\daterevised{10 January 2023} % Only for the journal Acoustics
\dateaccepted{12 January 2023}
\datepublished{}
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

\usepackage{gensymb}
%\usepackage{amsmath}
\usepackage{accents}
%\usepackage{multirow}
\usepackage{xspace}
\usepackage{subcaption}
\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\A}{\mbox{\large\ensuremath{\mathsf{A}}}}
\DeclareRobustCommand{\B}{\mbox{\large\ensuremath{\mathsf{B}}}}
\DeclareRobustCommand{\C}{\mbox{\large\ensuremath{\mathsf{C}}}}
\DeclareRobustCommand{\Dev}{\mbox{\Large\ensuremath{\mathsf{s}}}}
\DeclareRobustCommand{\Sig}{\mbox{\Large\ensuremath{\sigma}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{{i.e.,}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\MSE}{\text{E}_\text{MS}}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Development and Implementation of an ANN Based Flow Law for Numerical Simulations of Thermo-Mechanical Processes at High Temperatures in FEM Software}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Development and Implementation of an ANN Based Flow Law for Numerical Simulations of Thermo-Mechanical Processes at High Temperatures in FEM Software}

@@

% Authors, for the paper (add full first names)
\Author{Olivier Pantal\'{e}\orcidA{}}

@@

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Olivier Pantal\'{e}}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Pantal\'{e}, O.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [XX] after \address if there is only one affiliation.)
\address[1]{Laboratoire Génie de Production, Institut National Polytechnique/Ecole Nationale d'Ingénieurs de Tarbes, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; Olivier.Pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Numerical methods based on finite element (FE) have proven their efficiency for many years in the thermomechanical simulation of forming processes.
Nevertheless, the application of these methods to new materials requires the identification and implementation of constitutive and flow laws within FE codes, which sometimes pose problems, particularly because of the strongly non-linear character of the behavior of these materials.
Computational techniques based on machine learning and artificial neural networks are becoming more and more important in the development of these models and help the FE codes to integrate more complex behavior.
In this paper, we present the development, implementation and use of an artificial neural network (ANN) based flow law for a GrC15 alloy under high temperature thermomechanical solicitations.
The flow law modeling by ANN shows a significant superiority in terms of model prediction quality compared to classical approaches based on widely used Johnson--Cook or Arrhenius models.
Once the ANN parameters have been identified on the base of experiments, the implementation of this flow law in a finite element code shows promising results in terms of solution quality and respect of the material behavior.}

% Keywords
\keyword{ANN flow law; constitutive behavior; radial return algorithm; numerical implementation; VUHARD ; GrC15; Abaqus Explicit}

@@

Numerical methods for simulating the behavior of structures subjected to high thermomechanical loads, as~in the case of the high-temperature forming of metallic materials, are generally based on the use of commercial finite element (FE) codes, such as Abaqus, or laboratory codes, such as DynELA~\cite{Pantale-2004}.
These FE codes are based on two types of equations: conservation equations and constitutive equations.
If the first equations are well established on the basis of physics and mechanics, it is not the same for the second type of equations: the constitutive equations.
Thus, in~a general way, the~conservation equations concern the fundamental principles of physics, such as the mass conservation law, the~momentum law (fundamental equation) and the energy law (declined as the first and second principles of thermodynamics).
By themselves, these laws are not sufficient to describe the behavior of a material or a structure subjected to thermomechanical solicitations because~the nature of the material’s behavior translated through the behavior laws is not included in the system previously proposed.
Therefore, for~each type of material, it is necessary to define behavior laws whose formulation is based on observation in~order to describe the behavior of this material under external forces.
The quality and the accuracy of the results of any numerical simulation depend on the choice of these behavior laws and on the ability of the user to identify the coefficients of these behavior laws for a given material by performing experiments under conditions close to those encountered during the real stress of the structure in service that one wishes to design~\cite{Dey-2007}.
Depending on the nature of the solicitations, these tests are based on quasi-static or dynamic tensile or compression tests, tests on thermomechanical simulators such as Gleeble~\cite{Lin-2009} or impact tests using gas launchers or Hopkinson bars~\cite{Kolsky-1949}.

In the thermomechanical simulation of forming processes, these behavior laws define the dependence~\cite{Lee-2006} of the flow stress of the material $\sigma^y$ as a function of the three input variables, which are the plastic strain $\varepsilon^p$, the~strain rate $\mdot\varepsilon$ and the temperature $T$ of the material, so that the general form of the flow law can be written with the following expression:
\begin{equation}
\sigma^y = f\left(\varepsilon^p,\mdot\varepsilon,T\right)\label{eq:GenFlow}
\end{equation}

These laws, due to the nature of materials and the phenomena involved~\cite{Lennon-2004, Zhang-2012} (work hardening, movement of dislocations, structural hardening, phase transformations, etc.) are highly non-linear, and their validity is restricted to a certain range of strains $\varepsilon$, strain rates $\mdot\varepsilon$ and temperatures $T$.
From the observations made, we can define two main classes of behavior laws: the flow laws based on physics and the empirical flow laws.
From the mechanics of continuous media and experimental tests and depending on the materials used, several flow models have been developed in the past, including the Johnson--Cook flow law~\cite{Johnson-1983, Johnson-1988}, the~Zerilli--Armstrong flow law~\cite{Zerilli-1987} and their respective derived \mbox{forms~\cite{Lin-2011, Li-2013, Zhang-2015, Zhou-2020, Jia-2021, Rule-1998, Lin2010, Muralli-2017, Cheng-2021}}, the~Hansel--Spittle~\cite{Hensel-1978, Chadha-2018} or the Arrhenius~\cite{Jonas-1969, He-2013, Liang-2022} flow laws, to~name only a few of the most widely used in the metal-forming processes at high temperature.
As an example, and~because it is widely used in numerical simulation of metal forming processes, the~equation that describes the Johnson--Cook flow law~\cite{Johnson-1983} is given as follows:
\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, and $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The Johnson--Cook model is the most widely used because it is simple to identify and use and has few parameters to determine~\cite{NematNasser-2003, Khan-2004}.

Once the choice has been made concerning the type of flow law to be used for a material, it is then necessary, from~a set of experimental tests carried out in the laboratory under conditions close to those of the structure in service, to~identify the parameters of these flow laws by machine learning methods based on approaches of minimization of the calculated experiment.
Therefore, the~use of the Johnson--Cook flow law defined by Equation~(\ref{eq:Johnson-Cook}) requires the identification of $5$ material~parameters.

The main problem that researchers are confronted with after the phase of realization of the experimental tests concerns the choice of the flow law to use according to the observations made on these test results.
This choice of flow law is also restricted by the FE code used and the availability of such flow laws.
Thus, a~user of the Abaqus FE code will turn more particularly to a Johnson--Cook~\cite{Johnson-1983} flow law, where it is natively implemented in this software.
The choice of another form of flow law, Zerilli--Armstrong, or~Arrhenius, for example, obliges the user to program himself the computation of the flow stress $\sigma^y$ of the material through a VUMAT subroutine in FORTRAN 77 as proposed by Gao et~al.~\cite{Gao-2007-FRT}, Ming et~al.~\cite{Ming-2018} for a Johnson--Cook flow law, or Liang et~al.~\cite{Liang-2022} for an Arrhenius type flow law with the following expression:
\begin{equation}
\sigma^y = \frac{1}{\alpha(\varepsilon)} \ln\left\{\left(\frac{Z(\varepsilon)}{A(\varepsilon)}\right)^{1/n(\varepsilon)} + \sqrt{1 + \left(\frac{Z(\varepsilon)}{A(\varepsilon)}\right)^{2/n(\varepsilon)}}\right\}
\label{eq:ArDef}
\end{equation}
with
\begin{equation}
Z(\varepsilon) = \mdot\varepsilon \exp{\left(\frac{Q(\varepsilon)}{RT}\right)}, \label{eq:ArZ}
\end{equation}
where $Z$ is the Zenner--Hollomon parameter~\cite{Zener-1944}, $Q(\varepsilon)$ is the apparent activation energy ($\text{J~mol}^{-1}$), $R$ is the universal gas constant ($8.314~\text{J~mol}^{-1} \text{K}^{-1}$).
$Q(\varepsilon)$, $A(\varepsilon)$, $\alpha(\varepsilon)$ and $n(\varepsilon)$ are expressed as a function of the strain $\varepsilon$ through polynomial functions of degree $m$ (varying from $1$ to $9$), which leads to the identification of up to $36$ material~parameters.

Implementing the flow law as a VUMAT FORTRAN subroutine requires the computation of the derivatives  $\partial\sigma^y/\partial\varepsilon^p$, $\partial\sigma^y/\partial\mdot\varepsilon$ and $\partial\sigma^y/\partial T$ of the flow stress $\sigma^y$, which can quickly become relatively complex as the complexity of the flow law increases, \ie the relative complexity of the Arrhenius flow law defined by Equations~(\ref{eq:ArDef}) and (\ref{eq:ArZ}), regarding the relative simplicity of the Johnson--Cook model defined by Equation~(\ref{eq:Johnson-Cook}), one can refer to the work proposed by Liang et~al.~\cite{Liang-2022} for details concerning this implementation using the safe version of the Newton--Raphson method proposed by Ming et~al.~\cite{Ming-2018}.
The choice of the flow law to use for a problem is therefore doubly guided by the behavior of the material on the one hand, but~a more important aspect is the list of flow laws implemented natively in the FE code we plan to use for the numerical simulation.
At this time, there is not yet a flow law generic enough to cover a wide range of material behavior that is simple to implement and~use.

As we have seen in the previous paragraph, the~choice of the flow law to use is guided mainly by the list of flow laws available in the finite element code used, and~very often, this choice is made at the expense of the quality of the model.
For example, Zhou et~al.~\cite{Zhou-2020}, proposed the identification of the flow law of a GCr15 alloy for a continuous casting bloom with heavy reduction application as introduced by Ji et~al.~\cite{Ji-2018}, who performed compression tests on this material.
In their study, Ji et~al.~\cite{Ji-2018} performed compression tests on GCr15 cylinders in a temperature range of $750~\celsius$ to $1300~\celsius$ in $50~\celsius$ steps, strain rates of $0.001~\ps$,  $0.01~\ps$ and $0.1~\ps$ and strains up-to $0.7$.
The results of these compression tests, plotted in Figure~\ref{fig:Zhou-OriginalData}, show a decrease in flow stress $\sigma^y$ with respect to an increase in the temperature $T$ and a increase of $\sigma^y$ with respect to an increase in the strain rate $\mdot\varepsilon$, as~in most metallic~materials.
\begin{figure}[H]
\includegraphics[width=0.9\columnwidth]{Figures/Zhou-OriginalData}
\caption{Original data extracted from the publication of Ji et~al.~\cite{Ji-2018}.}
\label{fig:Zhou-OriginalData}
\end{figure}
The evolution of the flow stress as a function of the plastic deformation shows the presence of a dynamic recrystallization (DRX) phenomenon within the material.
This phenomenon is an additional non-linearity of this type of material compared to other materials, mainly because of high temperatures and low strain rates, which should be considered when describing the material behavior.
As stated in the publication of \mbox{Zhou et~al.~\cite{Zhou-2020}}, depending on the flow model used---Johnson--Cook, modified Zerilli--Armstrong, Arrhenius or new modified Johnson--Cook---the~fidelity of considering the real behavior varies widely with the complexity of the flow model, which includes between $5$ parameters for the Johnson--Cook model and~$16$ parameters for the Arrhenius model.
Thus, and~for the input data provided by Ji et~al.~\cite{Ji-2018}, the~two most common models, Johnson--Cook and Zerilli--Armstrong do not correctly describe the material behavior.
Only the modified Johnson--Cook and Arrhenius models can describe correctly the behavior of the material during the compression process.
Unfortunately, and~this is not part of their study, if~these last two models are satisfactory from a theoretical point of view, from~a practical point of view for the user of a FE code such as Abaqus, it will be necessary to carry out a numerical implementation in a FORTRAN 77 VUMAT subroutine of the modified Johnson--Cook flow law or the Arrhenius law as carried out by a few authors~\cite{Liang-2022, Gao-2007-FRT, Ming-2018} to use these laws for numerical simulation.
This requires a certain expertise in the development and implementation of flow laws, which is not available to all users of the Abaqus FE~code.

From this observation, and~from the necessity to select a flow law for a type of material, then to identify the parameters of this flow law according to experimental tests, and~finally to implement this flow law as a user subroutine in FORTRAN in the Abaqus FE code, we recently proposed in Pantalé et~al.~\cite{Pantale-2021} an alternative approach based on the ability of artificial neural networks (ANNs) to behave as universal approximators as reported by Minsky et~al.~\cite{Minsky-1969} and Hornik et~al.~\cite{Hornik-1989}.
In fact, artificial neural networks can solve problems that are difficult to conceptualize using traditional computational methods.
Unlike a classical approach based on a regression method, an~ANN does not need to know the mathematical form of the model it seeks to reproduce; hence, we do not need anymore to postulate the mathematical form of the constitutive equation to use it in a FE simulation using this kind of approach.
Using a neural network instead of an analytical constitutive law can lead to a bias related to the validity of the answers according to the domain of use and the learning domain.
Thus, if~ANNs are efficient for the interpolation of results inside the learning domain, their behavior outside of it is not controlled.
Therefore, if~the input values are far from those provided during the training, the~outputs can be far from the physical reality of the process.
It is, of~course, the~same for analytical laws when modeling non-linear behavior, but~if the choice of the model is made properly, based on physical considerations, they will provide results closer to reality than the ANN model.
Therefore, care should be taken when using ANN-based flow laws, and the validity of the model input data should always be~verified.

Implementing ANNs for plasticity in thermomechanics has been studied, and a review of the literature can be found, for example, in the work of Gorji et~al.~\cite{Gorji-2020} concerning the use of recurrent neural networks, in that of~Jamli et~al.~\cite{Jamli-2019-SNN} concerning their application in finite element analysis of metal forming processes, or~in that of Jiao et~al.~\cite{Jiao-2020} concerning the applicability to meta-materials and their characterization.
A distinction must be made between ANN-based flow models (the focus of this study) and ANN-based constitutive models.
Both approaches have been studied by many researchers during the last thirty years.
Ghaboussi~\cite{Ghaboussi-1991} proposed an ANN-based constitutive model for concrete under monotonic biaxial loading and cyclic uniaxial loading.
They extended their work by introducing adaptive and auto-progressive networks in~\cite{Ghaboussi-1998, Ghaboussi-1998-NNA}, where the architecture of the network evolves during the learning phase to better learn the complex stress--strain behavior of the materials using a global load-deflection response, where the evaluation of the flow stress of the material computed by the ANN is combined with a radial return algorithm.
Lin et~al.~\cite{Lin-2008} proposed an ANN to predict the flow stress of 42CrMo4 steel in hot compression tests on a Gleeble thermomechanical device and showed a very good correlation between the experimental results and the model predictions.
Ashtiani et~al.~\cite{Ashtiani-2016} compared the predictive capabilities of an ANN versus an analytical model for Johnson--Cook, Arrhenius, and~strain-compensated Arrhenius laws and concluded that the neural network had better efficiency and accuracy in predicting the hot behavior of the Al--Cu--Mg--Pb~alloy.
